Concurrent Programming in Harmony

### 2021-12-25 book/paper.tex
Pass over Ch 19

To implement a \emph{No Hold and Wait} solution, a philosopher would need a
way to lock both the left and right forks at the same time.  Locks do not
have such an ability, and neither do semaphores. so we re-implement the
Dining Philosophers using condition variables that allow one to wait for
arbitrary application-specific conditions.
%
\autoref{fig:dinerscv} demonstrates how this might be done.
We use a single mutex for the diners, and, for each fork, a boolean
and a condition variable.  The boolean indicates if the fork has been
taken.
Each diner waits if either the left or right fork is already taken.
But which condition variable to wait on?
The code demonstrates an important technique to use when waiting for
multiple conditions.
\index{multiple conditions, waiting on}%
The condition in the <{while}> statement is the negation of the
condition that the diner is waiting and consists of two disjuncts.
Within the <{while}> statement,
there is an <{if}> statement for each disjunct.
The code waits for either or both forks if necessary.  After that, it goes
back to the top of the <{while}> loop.

>>>>

To implement a \emph{No Hold and Wait} solution, a philosopher would need a
way to lock both the left and right forks at the same time.  Locks do not
have such an ability, and neither do semaphores. so we re-implement the
Dining Philosophers using condition variables that allow one to wait for
arbitrary application-specific conditions.
%
\autoref{fig:dinerscv} demonstrates how this might be done.
We use a single mutex for the diners, and, for each fork, a boolean
and a condition variable.  The boolean indicates if the fork has been
taken.
Each diner waits if either the left or right fork is already taken.
But which condition variable to wait on?
The code demonstrates an important technique to use when waiting for
multiple conditions.
\index{multiple conditions, waiting on}%
The condition in the <{while}> statement is the negation of the
condition that the diner is waiting for and consists of two disjuncts.
Within the <{while}> statement,
there is an <{if}> statement for each disjunct.
The code waits for either or both forks if necessary.  After that, it goes
back to the top of the <{while}> loop.
